Kaggle-in-class Data Challenges Can Boost Student Learning

### 2021-01-06 paper-kaggle.Rmd
response t oreeview

```{r Monash_quiz, fig.cap = "\\label{fig:Monash_quiz}Beeswarm plots of undergraduate (ST-UG) and postgraduate (ST-PG) students quizzes during the semester. The scores are very similar, although undergraduates have a longer lower tail.", fig.height=6, fig.width=6}
library(tidyverse)
library(gridExtra)
library(ggbeeswarm)
library(forcats)
quiz <- read_csv(file="data/quiz_scores_by_unit_2420_5242.csv")

@@

@@

After collecting the survey from the students we were told that the questions about students engagement were positively worded. This may have potentially led to some bias. An improved way could be to ask directly about student's engagement, e.g. "How would you rate your level of engagement in this course?" with set answer options of "not at all engaged" -- up to "extremely engaged" with several choices in between. Another improvement could be asking ST-UG  students that didn't take part in the competition about their level of engagement and compare the answers with other students of ST-PG. We acknowledge that the differences in the engagement levels may not necessarily be a result of participation in the competition but it is still an interesting aspect.

The survey was not anonymous. However, the results became available to the lectures only after all the grades were realised to the students. This point was emphasized in the instructions to the students at the beginning of the survey.

@@

Choosing the metric upon which to evaluate the model is another decision. Our advice is to keep it simple, so you, and the students, can understand the student scores. If you are running a regression challenge, then the "Root Mean Squared Error (RMSE)" is a good choice. If it is a classification challenge, then "Categorization Accuracy", the percent of correct classifications, is reasonable.

>>>>

```{r Monash_quiz, fig.cap = "\\label{fig:Monash_quiz}Beeswarm plots of undergraduate (ST-UG) and postgraduate (ST-PG) students quizzes during the semester. The scores are very similar, although undergraduates have a longer lower tail.", fig.height=6, fig.width=6, eval=FALSE}
library(tidyverse)
library(gridExtra)
library(ggbeeswarm)
library(forcats)
quiz <- read_csv(file="data/quiz_scores_by_unit_2420_5242.csv")

@@

# investigate similarity/differences between scores
quiz <- quiz %>%
  filter(score > 0)

ggplot(quiz, aes(x=score^4, colour=unit, fill=unit)) +
  geom_density(alpha=0.5) +
  facet_grid(unit~quiz, scales="free") + 
  xlab("") + ylab("Score (%)") +
  theme(legend.position="none")

@@

After collecting the survey from the students we realized that the questions about student engagement were positively worded, which has the potential to for bias in response. An improved wording would be to ask neutrally about engagement, e.g. "How would you rate your level of engagement in this course?" with set answer options of "not at all engaged" -- up to "extremely engaged" with several choices in between. Another improvement could be asking ST-UG  students that didn't take part in the competition about their level of engagement and compare the answers with other students of ST-PG. We acknowledge that the differences in the engagement levels may not necessarily be a result of participation in the competition but it is still an interesting aspect.

The survey was not anonymous. However, the results became available to the lecturers only after all the grades were realised to the students. This point was emphasized in the instructions to the students at the beginning of the survey.

@@

Choosing the metric upon which to evaluate the model is another decision. Our advice is to keep it simple, so you, and the students, can understand the student scores. If you are running a regression challenge, then the "Root Mean Squared Error (RMSE)" is a good choice. If it is a balanced class classification challenge, then "Categorization Accuracy", the percent of correct classifications, is reasonable.
